---
title: "serpico2:usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{serpico2:usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                       collapse = TRUE) #, comment = "#>")
knitr::opts_knit$set(root.dir = '../')
options(knitr.table.format = function() {
  if (knitr::is_latex_output()) 
    "latex" else "pandoc"
})
# options(scipen=999)
```

```{r pkg}
library(serpico2)
```

```{r read, include = FALSE}
knitr::read_chunk("R/run_model.R")
run <- TRUE
```

## Simulating a sample dataset
We start by simulating a sample dataset using function `simulate_mock_data`. By default it represents seropositivity measures in distinct individuals stratified by sex, age and region, and over 3 time periods. A baseline prevalence level is set for the second period and risks of infection are varied by period and individual covariates. Test positivity is a function of sensitivity and specificity. In this simulated example and for simplicity, response rate is considered fixed for now.

```{r simsample}

```

Sample looks like so:
```{r }
rbind(head(d0), tail(d0))
```

And we can assess observed prevalence (test positivity) by categories

```{r}
vars = c("time", "sex", "age", "reg")
print( lapply(setNames(vars, vars), function(v){
      round( tapply(d0[,"res"], d0[,v], mean), 3)
    }) )
```

We will also need poststratification population counts and region names (`poststrat` and `code_region` datasets). Following actual study input and results, we exclude one region (Mayotte).
```{r extdata}

```

## Estimating prevalence
### MCMC
Then, posteriors of regression parameters are estimated by MCMC
```{r fit}

```
### Post-stratification
Next, post-stratified counts of positive in the population are calculated
```{r poststratification}

```

### Processing iterations
Finally, results are summarized over iterations to estimate overall and stratified prevalence
```{r summarize}

```

### Results by period
```{r}
knitr::kable(res)
```


